
Cloud computing is a computing model, refers to the on-demand delivery of IT resources and applications via the Internet with pay-as-you-go pricing. The cloud mode has 5 essential characteristics, 3 service models and 4 deployment models. In this chapter, I will talk about the property of cloud. 
\begin{itemize}
	\item Essential Characteristics:
		\begin{itemize}
			\item On-demand self-service: A user can individually provision computing capabilities, such as server time and network storage and this process need automatically without requiring human interaction.
			\item Broad network access : The availability access over the network and many different device allow access through standard mechanisms. 
			\item Resource pooling : All of resource are centralize to service for customer. And the tenant can’t know the information about resource.
			\item Rapid elasticity: Provisioning is rapid and scales out or is based on need. This characteristics increase the use of resource more flexible. 
			\item Measured service: The cloud need it to manage the service and billing. Beside, cloud automatic control and optimize resource use by leveraging a metering. Resource can be collected , monitored, reported and billing. This ensure the user can pay per use. 
		\end{itemize}

\item Service Models:
	\begin{itemize}
		\item Software as a Service(Saas): The capacity provide to the user use the software running on the cloud . The app can  accessible from client through web interface , API or program interface.
		\item Platform as a Service (PaaS): The capacity provided to the user deploy the application onto the cloud infrastructure base on  programming languages, libraries, services or tools supported. The client does not manage or control the underlying cloud infrastructure like Sass but has control over the deployed applications and possibly configuration settings for the application-hosting environment infrastructure consumer-created. Some of  PaaS is: Heroku, Google App Engine
		\item Infrastructure as a Service (IaaS): The capacity provided the infrastructure such as instance or vitural machine to the consumer so that user can run the app or deploy operation system . Some of IaaS is : Amazon EC2, Google Compute Engine, Rackspace Cloud, Windows Azure, Digital Ocean.
	\end{itemize}

\item Deployment Models:
	\begin{itemize}
		\item Private cloud: A private cloud operates for a single organization
		\item Public cloud: It build to provide the service for anyone on the internet. Public cloud has an infrastructure that is available to the general public and is likely owned by a cloud services company.  
		\item Hybrid cloud: A hybrid cloud is a combine of public cloud and private cloud.
	\end{itemize}
\end{itemize}